### 2023-04-03 main.tex
abs

\sum_{i=1\,:\, i\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(2+L)}

@@

@@

\subsection{One points correlations of the non-integrable multi-speceis stirring process on a chain}

@@

\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-i_{a}}a_{i_{1},\ldots,i_{a}}(\bm{\xi})

@@

    a_{i_{a}}(\bm{\xi})=\mathbb{P}\left(\xi(\infty)=\sum_{a=2}^{N}\left(i_{a}\delta_{0}+(|\xi_{a}|-i_{a})\delta_{L+1}\right)| \xi_{0}=\xi\right)

>>>>

\sum_{i=1\,:\, i\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(2+L)}

@@

\textbf{Remark}: using the Binomial Theorem we rewrite the \eqref{exactCorrelations} as
	\langle n^{y_{1}}_{s_{1}},\ldots,n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})g_{k}(c_{k},\ldots,c_{m})

@@

\subsection{One points correlations of the non-integrable multi-speceis stirring process on a chain[To check, something could be wrong]}

@@

\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-i_{a}}a_{i_{1},\ldots,i_{N}}(\bm{\xi})

@@

    a_{i_{1},\ldots,i_{N}}(\bm{\xi})=\mathbb{P}\left(\xi(\infty)=\sum_{a=2}^{N}\left(i_{a}\delta_{0}+(|\xi_{a}|-i_{a})\delta_{L+1}\right)| \xi_{0}=\xi\right)
